Figures

### 2019-07-23 figures/07_model-selection.Rmd
towards labeling and coloring

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty))

text_colors <- ifelse(gg_tp$signif == 0, "black", "red")
(gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  theme(axis.text.y = element_text(size = 12, color = text_colors)) +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) + 
  ggtitle("TP ~ Slope") +
  xlab(""))
```

>>>>

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Land-use cover", "Buffer composition", 
                                      "Lake")))) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

text_colors <- rev(ifelse(gg_tp$signif == 0, "black", "red"))
# cbind(text_colors, as.character(gg_tp$pretty))

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.2) +
  geom_rect(ymin = -0.6, ymax = -1.5, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "white") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 1.1, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::format_format(scientific = FALSE)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized FE slope") + theme(legend.position = 0) + 
        ggtitle("TP ~ Slope") + xlab("")

gp <- ggplotGrob(gg_tp_fe)
facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
x.var         <- sapply(ggplot_build(gg_tp_fe)$layout$panel_scales_x,
                function(l) length(l$range$range))
gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
gg_tp_fe <- ggplotify::as.ggplot(gp)
gg_tp_fe
```
